---
title: "linear model from Web"
author: "Juliet Clark"
date: "Summer 2024 "
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 
#Methods
All variables are numerical therefor we use the numerical numerical files. 

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS


### descriptive results
```{r}
plot(SIMS~ARM,data=data)
```

This plot shows the arm strength increasing as the stimulation value inceases. 

### graphical results

```{r}
plot(SIMS~ARM,data=data)
```

### Numerical results

```{r}
cor(SIMS~ARM, data=data)
```
This correlation shows that the arm strength increases and there is a positive trend with SIM.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

Intercept p-value <0.05
->significant "different from 0"
Coefficient ARM P-Val <0.05 -> ARM is significant "ARM works to redict SIMS"

#### Predict at target point

```{r}
newdata = data.frame(ARM = 88, GRIP=99)
predict(model.1, newdata, interval='pred')
```

The SIMS prediction for ARM=88 is 0.71, the predicting interval is (-1.73, 3.14) 

#### scatterplot with model fit

```{r}
plot(SIMS~GRIP, data=data)
```

There seems to be a positive correlation. 

## Model 2 SIM~GRIP

```{r}
cor(SIMS~GRIP, data=data)
```

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
 
```{r}
model.1 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```

```{r}
plot(SIMS~GRIP,data=data)
abline(model.1, col='red')
```

Intercept p-value <0.05
->significant "different from 0"
Coefficient ARM P-val <0.05 -> ARM is significant "ARM works to predict SIMS
#### predict model.2 at target point

```{r}
newdata = data.frame (ARM = 88, GRIP=94)
predict (model.1, newdata, interval='pred')
```
The SIMS prediction is 0.54, the interval is (-3.11, 2.04)

## Model 3 SIM~ARM+GRIP

```{r}
model.3 = lm(SIMS=ARM_GRIP,data=data)
summary (model.3)
```
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.1 <- lm(SIMS~ARM + GRIP, data=data)
summary.lm(model.1)
```
```{r}
plot(SIMS~ARM + GRIP,data=data)
abline(model.1, col='red')
```

Intercept p-value <0.05
->significant "different from 0"
Coefficient ARM P-val <0.05 -> ARM is significant "ARM works to predict SIMS"


#### predict model.3 at target point

```{r}
newdata = data.frame (ARM = 88, GRIP=94)
predict (model.1, newdata, interval='pred')
```

The SIMS prediction for ARM is 0.14. The predicting interval is (-2.13, 2.43)

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

